Coherent optical association of a single molecule -- Supplemental material

### 2020-11-03 sm.tex
Update on Overleaf.

Our Raman transfer scheme differs from typical Raman transfers, for instance between hyperfine states in atoms, in two key ways.

@@

\bibliography{master-ref}
\end{document}

>>>>

In our system, the separation in energy between the initial and target state is much smaller than the single photon detuning $\Delta$ from the intermediate state. Thus, there is significant cross coupling for the scattering rate and light shift, where each state is coupled to the excited state by the power in both beams. Under these conditions, the scattering rate and light shift is proportional to the total power $P_{\text{tot}} = P_m + P_a$, where $P_{m} (P_{a})$ is the power in the beam that addresses the molecular (atomic) state. The Raman Rabi frequency is proportional to $\sqrt{P_mP_a} $. With a fixed total power and thus fixed scattering rate, the Raman Rabi frequency is maximized by maximizing $\sqrt{P_m(P_{\text{tot}} - P_m)}$, which is achieved when $ P_m = P_a = P_{\text{tot}}/2$.

\section{Raman Transfer with Many Excited States}

\section{Calculating Matrix Elements with Coupled Channel Ground State}

@@

\bibliography{master_ref}
\end{document}
